What do incoming university students believe about open science practices in

### 2021-02-10 analysis/Manuscript.Rmd
start on demographics

# convert factors to characters as needed
df$university <- as.character(df$university)
df$degree <- as.character(df$degree)
df$major <- as.character(df$major)
df$major <- as.character(df$major)
df$uni_country <- as.character(df$uni_country)
df$nationality <- as.character(df$nationality)

@@

# I fell down a massive git hub hole, so I'll make progress on this tomorrow!

@@

df$eligibility <- factor(df$eligibility)
df$eligibility_lab <- factor(df$eligibility_lab)

@@

# filter(eligibility %in% 1)

@@

>>>>

# convert factors to characters as needed
df$university <- as.character(df$university)
df$degree <- as.character(df$degree)
df$major <- as.character(df$major)
df$major <- as.character(df$major)
# df$uni_country <- as.character(df$uni_country)
# df$nationality <- as.character(df$nationality) [i think these should be factors]

@@

# all participants
n_all <- nrow(df)

@@

age <- df %>%
  dplyr::count(age_lab)

@@

n <- el[5,2]
# filter(eligibility %in% 1)

# gender --> need to run through gendercoder
# high school status
# high school psyc 
# country of university 
# country of nationality
# whether parents' attended uni

@@

Of those who started the survey (*n* = `r n_all`), we screened out participants who 
were not eligible to participate based on our preregistration. Specifically, 
we screened out people who were younger than 18 years of age (*n* = `r age[1,2]`). 
We also screened out individuals who had already started a psychology unit at a
university, regardless of whether they completed it (*n* = `r el[1,2] + el[3,2] + el[4,2]`); 
were not enrolled in a psychology unit at a university (*n* = `r el[2,2]`); or did 
not answer this question (*n* = `r el[6,2]`). The remaining `r el[5,2]` participants
were eligible based on starting their first unit of study in psychology at 
a university within the next month. For those individuals who were screened out, 
our Qualtrics program automatically directed them to the debriefing form.

Of the remaining `r n` participants, most reported that they were
18-24 years old (*n* = `r age[2,2]`), `r age [3,2]` 
reported that they were 25-34 years old, `r age [4,2]` were 35-44 years old,
`r age [5,2]` were 45-54 years old, `r age [6,2]` were 55-64 years old, and
`r age [7,2]` were 65 years or older. A small number of participants did not 
report their age(*n* = `r age [8,2]`).

```{r qual responses}

# once qual responses are coded, I will need to return here to 
 # include details about which univrsity the participant is enrolled in
 # name of qualification
 # major
